

\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[all]{xy}


\usepackage{amsmath,amsthm,amssymb,color,latexsym}
\usepackage{geometry}
\geometry{letterpaper}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{svg}
\usepackage{changepage}

\newtheorem{problem}{}%Problem}

\newenvironment{solution}[1][\it{Solution}]{\textbf{#1. } }{$\square$}


\begin{document}
\noindent \Large \textbf{COSC-4380.001}  \hfill \textbf{Final Exam}  \hfill \textbf{\today}\\

\vspace{0cm}

\textbf{Name:}
\hrulefill

\vspace{0.2cm}
\Large
\textbf{Instructions:}
\begin{itemize}
    \item Closed notes
    \item Calculators allowed
\end{itemize}

%\vspace{.5cm}

\section{Prime Numbers}

\subsection{Approximately \underline{what fraction} of numbers below $2^{1157}$ are prime?}

\vspace{7cm}

\subsection{Approximately \underline{how many} numbers below $2^{1157}$ are prime?}

\newpage

\subsection{Approximately \underline{how many} numbers between $2^{1157}$ and $2^{1153}$ are prime?}

\vspace{8cm}

\section{Moore's Law}

\subsection{If a cryptosystem took 120,000,000 years to brute force on brand new equipment in 1961, \underline{how long} will it take to break on equivalent-value new equipment in 2002?}

\newpage

\subsection{In 1979, equipment of a given value could brute-force a cryptosystem in 138,000,000 years.  In \underline{what year} will new equipment of equivalent cost be able to break the same crypto in just 30 days?}

\vspace{9cm}

\subsection{In 1965, equipment that could brute-force a cryptosystem in 25 days cost \$130,000,000.  In \underline{what year} will that equipment cost just \$1000?}

\newpage

\section{Decrypt the columnar transposition: \\ UINLLCSAAATOOXUIPTLWRMTLHEITSVSYRUW \\ using the key 9721654.}

\vspace{9cm}

\textbf{Problems 5-8 rely on the following scenario:}

\textbf{In an alternative universe, computers and encryption do not exist.  Instead, everyone has access to a magic device that produces an infinite number of physical items on command.  In order to send messages to your friend in secret, you can use the device to produce an indestructible, locking tube that you can store the rolled-up message inside.  You can then send the tube by courier to your friend, who can open the tube and read the message so long as you both agreed upon a key at some point in the past.  There is no way to open the tube without the proper key, and the magical keys made by the machine can have upwards of $10^{100}$ possible bittings, making it infeasible to guess the correct key.}

\end{document}
