

\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[all]{xy}


\usepackage{amsmath,amsthm,amssymb,color,latexsym}
\usepackage{geometry}
\geometry{letterpaper}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{svg}
\usepackage{changepage}

\newtheorem{problem}{}%Problem}

\newenvironment{solution}[1][\it{Solution}]{\textbf{#1. } }{$\square$}


\begin{document}
\noindent \Large \textbf{COSC-4380.001}  \hfill \textbf{Final Exam}  \hfill \textbf{\today}\\

\vspace{0cm}

\textbf{Name:}
\hrulefill

\vspace{0.2cm}
\Large
\textbf{Instructions:}
\begin{itemize}
    \item Closed notes
    \item Calculators allowed
\end{itemize}

%\vspace{.5cm}

\section{Prime Numbers}

\subsection{Approximately \underline{what fraction} of numbers below $2^{1063}$ are prime?}

\vspace{7cm}

\subsection{Approximately \underline{how many} numbers below $2^{1063}$ are prime?}

\newpage

\subsection{Approximately \underline{how many} numbers between $2^{1063}$ and $2^{1053}$ are prime?}

\vspace{8cm}

\section{Moore's Law}

\subsection{In 1951, equipment of a given value could brute-force a cryptosystem in 102,000,000 years.  In \underline{what year} will new equipment of equivalent cost be able to break the same crypto in just 30 days?}

\newpage

\subsection{In 1965, equipment that could brute-force a cryptosystem in 21 days cost \$95,000,000.  In \underline{what year} will that equipment cost just \$1000?}

\vspace{9cm}

\subsection{If a cryptosystem could be brute-forced in 1 day on brand new equipment costing \$110,000,000,000 in 1980, \underline{how much} would the same equipment cost if purchased in 2004?}

\newpage

\section{Decrypt the columnar transposition: \\ RIASXCIRODEYOTLIMNACUSTUOSTPTL \\ using the key 843725.}

\vspace{9cm}

\textbf{Problems 5-8 rely on the following scenario:}

\textbf{In an alternative universe, computers and encryption do not exist.  Instead, everyone has access to a magic device that produces an infinite number of physical items on command.  In order to send messages to your friend in secret, you can use the device to produce an indestructible, locking tube that you can store the rolled-up message inside.  You can then send the tube by courier to your friend, who can open the tube and read the message so long as you both agreed upon a key at some point in the past.  There is no way to open the tube without the proper key, and the magical keys made by the machine can have upwards of $10^{100}$ possible bittings, making it infeasible to guess the correct key.}

\end{document}
