

\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[all]{xy}


\usepackage{amsmath,amsthm,amssymb,color,latexsym}
\usepackage{geometry}
\geometry{letterpaper}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{svg}
\usepackage{changepage}

\newtheorem{problem}{}%Problem}

\newenvironment{solution}[1][\it{Solution}]{\textbf{#1. } }{$\square$}


\begin{document}
\noindent \Large \textbf{COSC-4380.001}  \hfill \textbf{Final Exam}  \hfill \textbf{\today}\\

\vspace{0cm}

\textbf{Name:}
\hrulefill

\vspace{0.2cm}
\Large
\textbf{Instructions:}
\begin{itemize}
    \item Closed notes
    \item Calculators allowed
\end{itemize}

%\vspace{.5cm}

\section{Prime Numbers}

\subsection{Approximately \underline{what fraction} of numbers below $2^{1128}$ are prime?}

\vspace{7cm}

\subsection{Approximately \underline{how many} numbers below $2^{1128}$ are prime?}

\newpage

\subsection{Approximately \underline{how many} numbers between $2^{1128}$ and $2^{1120}$ are prime?}

\vspace{8cm}

\section{Moore's Law}

\subsection{If a cryptosystem could be brute-forced in 1 day on brand new equipment costing \$130,000,000,000 in 1956, \underline{how much} would the same equipment cost if purchased in 2003?}

\newpage

\subsection{In 1957, equipment that could brute-force a cryptosystem in 13 days cost \$70,000,000.  In \underline{what year} will that equipment cost just \$1000?}

\vspace{9cm}

\subsection{If a cryptosystem took 108,000,000 years to brute force on brand new equipment in 1978, \underline{how long} will it take to break on equivalent-value new equipment in 2012?}

\newpage

\section{Decrypt the columnar transposition: \\ RMTLTUINLDSYRUTCSAAKTOOCWIPTWYEITST \\ using the key 5963187.}

\vspace{9cm}

\textbf{Problems 5-8 rely on the following scenario:}

\textbf{In an alternative universe, computers and encryption do not exist.  Instead, everyone has access to a magic device that produces an infinite number of physical items on command.  In order to send messages to your friend in secret, you can use the device to produce an indestructible, locking tube that you can store the rolled-up message inside.  You can then send the tube by courier to your friend, who can open the tube and read the message so long as you both agreed upon a key at some point in the past.  There is no way to open the tube without the proper key, and the magical keys made by the machine can have upwards of $10^{100}$ possible bittings, making it infeasible to guess the correct key.}

\end{document}
